\documentclass{article}
\makeatletter
\def\partbody{This partition paragraph exercises the typesetting pipeline with mixed content including mathematical expressions such as $\alpha_{n} + \beta_{n} = \gamma_{n}$ and the recurrence $a_{n+1} = a_n + n$ to establish meaningful compilation workload for parallel benchmarking. A second sentence revisits deterministic page construction, numbering, and paragraph breaking while mentioning the summation $\sum_{k=1}^{n} k = \frac{n(n+1)}{2}$ and the ratio $\frac{s_n}{n + 1} = n$. A third sentence keeps the content stable across job counts by repeating predictable prose about counters, references, and layout decisions so each partition contributes measurable compilation work. }
\def\partworkload{%
  \@for\pitem:=a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a\do{%
    \partbody
    \partbody
    \[
    \frac{s_n}{n + 1} = n
    \]
    \begin{equation}
    s_n = n^2 + n
    \end{equation}
  }%
  \@for\pitem:=a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a,a\do{%
    \partbody
    \partbody
    \[
    \frac{s_n}{n + 1} = n
    \]
    \begin{equation}
    s_n = n^2 + n
    \end{equation}
  }%
}
\makeatother
\begin{document}
\section{Overview}
This mixed article includes multiple section structures.
\makeatletter
\partworkload
\makeatother

\subsection{Inputs}
Inputs are listed here for the mixed partition case.
\makeatletter
\partworkload
\makeatother

\section{Details}
The details section contains a short list.
\begin{itemize}
\item First mixed item
\item Second mixed item
\end{itemize}
\makeatletter
\partworkload
\makeatother

\section{Math}
Inline math $x^2$ and display math follow.
\[
\frac{a}{b}
\]
\makeatletter
\partworkload
\makeatother

\section{References}\label{sec:references}
This section can be referenced from later material.
\makeatletter
\partworkload
\makeatother

\section{Appendix}
See Section \ref{sec:references} for the earlier reference target.
\makeatletter
\partworkload
\makeatother
\end{document}
